Implementation of poloidal density variation in collision operator

### 2019-03-05 doc/manual/version3/inputParameters.tex
Substantial revision to manual

\newcommand{\param}[5]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#1}{#1}}\\{\it Type}: #2\\{\it Default}: #3\\{\it When it matters}: #4\\{\it Meaning}: #5}}
\newcommand{\ssparam}[4]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#1}{#1}}\\{\it Type}: #2\\{\it When it matters}: #3\\{\it Meaning}: #4}}
\newcommand{\PETScParam}[2]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries #1}\\{\it Meaning}: #2}}
\newcommand{\myhrule}{{\setlength{\parindent}{0cm} \hrulefill }}

@@

{\ttfamily RHSMode} = 2: Solve for 3 right-hand sides to get the 3$\times$3 transport matrix. Presently implemented only for 1 species.\\

{\ttfamily RHSMode} = 3: Solve for the 2$\times$2 monoenergetic transport coefficients. When this option is chosen, \Nx~is set to 1 and only 1 species is used. \\

{\ttfamily RHSMode} = 4: Solve the adjoint equation to compute derivatives at constant $E_r$. Options related to the adjoint solve are detailed in section \ref{sec:adjointOptions}. {\ttfamily RHSMode} = 4 must be used with \parlink{includePhi1}=\false, \\ \parlink{EParallelHat}\texttt{=0}, \parlink{magneticDriftScheme}\texttt{>0}, \parlink{constraintScheme}\texttt{=-1} or 1, and \\ \parlink{collisionOperator}\texttt{=0}. \\

{\ttfamily RHSMode} = 5: Solve the adjoint equation to compute derivatives at the ambipolar $E_r$. Options related to the adjoint solve are detailed in section \ref{sec:adjointOptions}. {\ttfamily RHSMode} = 5 must be used with \parlink{includePhi1}=\false, \parlink{EParallelHat}\texttt{=0}, \parlink{magneticDriftScheme}\texttt{>0}, \parlink{constraintScheme}\texttt{=-1} or 1, and \\ \parlink{collisionOperator}\texttt{=0}.\\

@@

\param{ambipolarSolve}
{Boolean}
{\false}
{When \parlink{RHSMode}==1, 4, or 5.}
{When \true, a root finding method will be used to find the ambipolar \parlink{Er}. All output parameters will be included at the ambipolar \parlink{Er}. Options related to this parameter are \parlink{NEr\_ambipolarSolve}, \parlink{Er\_search\_tolerance\_dx}, \parlink{Er\_search\_tolerance\_f}, \parlink{ambipolarSolveOption}, \parlink{Er\_min}, and \parlink{Er\_max}.}

\param{NEr\_ambipolarSolve}
{integer}
{20}
{When \parlink{ambipolarSolve} == \true.}
{Maximum number of solves to allow while finding the ambipolar \parlink{Er}.}

\param{Er\_search\_tolerance\_dx}
{real}
{1.d-8}
{When \parlink{ambipolarSolve} == \true and \parlink{ambipolarSolveOption}/=2.}
{Tolerance used for ambipolar solve. If step size in \parlink{Er} falls below \parlink{Er\_search\_tolerance\_dx}, the ambipolar solve completes successfully. Note that this is not used for \parlink{ambipolarSolveOption}==2.}

\param{Er\_search\_tolerance\_f}
{real}
{1.d-10}
{When \parlink{ambipolarSolve} == \true.}
{Tolerance used for ambipolar solve. If the radial current,
\begin{gather}
J_r = \sum_s \texttt{Zs}(s) \texttt{particleFlux\_vm\_rN}(s),
\end{gather}
falls below \parlink{Er\_search\_tolerance\_f}, the ambipolar solve completes successfully.}

\param{ambipolarSolveOption}
{integer}
{1}
{When \parlink{ambipolarSolve} == \true.}
{Indicates which root solving algorithm to use for ambipolar solve. If \parlink{ambipolarSolveOption}==1 a Newton bisection method is used, \parlink{ambipolarSolveOption}==2 a Brent method is used, and if \parlink{ambipolarSolveOption}==3 a Newton method is used. If \parlink{ambipolarSolveOption}==1 or 3, an adjoint method will used to compute the $\partial J_r/\partial E_r$, so must be used with \parlink{includePhi1}==\false, \parlink{EParallelHat}==0, \parlink{magneticDriftScheme}>0, \parlink{constraintScheme}==-1 or 1, and \parlink{collisionOperator}==0.}

\param{Er\_min}
{real}
{-100}
{When \parlink{ambipolarSolve} == \true and \parlink{ambipolarSolveOption} /= 3. }
{Minimum value of \parlink{Er} used to bracket the ambipolar root. }

\param{Er\_max}
{real}
{100}
{When \parlink{ambipolarSolve} == \true and \parlink{ambipolarSolveOption} /= 3. }
{Maximum  value of \parlink{Er} used to bracket the ambipolar root. }

@@

{\ttfamily geometryScheme}==1: Use the following 3-helicity model:\\
\begin{eqnarray}
\label{eq:Bmodel}
B(\theta,\zeta)/\bar{B} 
&=& (\mbox{\parlink{B0OverBBar}}) [1 + (\mbox{\parlink{epsilon\_t}}) \cos(\theta) \\
&& + (\mbox{\parlink{epsilon\_h}}) \cos((\mbox{\parlink{helicity\_l}}) \theta - (\mbox{\parlink{helicity\_n}}) \zeta) \nonumber \\
&&  + (\mbox{\parlink{epsilon\_antisymm}}) \nonumber \\
&& \times \sin((\mbox{\parlink{helicity\_antisymm\_l}}) \theta - (\mbox{\parlink{helicity\_antisymm\_n}}) \zeta)] \nonumber
\end{eqnarray}

@@

{\ttfamily geometryScheme}==12: Read the IPP {\ttfamily .bc} format Boozer-coordinate file specified in \parlink{equilibriumFile} below. 
The file is assumed to be stellarator-\emph{asymmetric}.

{\ttfamily geometryScheme}==13: Read Boozer geometry from the {\ttfamily geometryParamters} namelist. Here the geometry parameters are specified by \parlink{boozer\_bmnc}, \parlink{GHat}, \parlink{IHat}, and \parlink{iota}. This has been implemented for use with STELLOPT for direct optimization of the Boozer spectrum. 
}

@@

{\ttfamily inputRadialCoordinate}==0: Use the flux surface specified by \parlink{psiHat\_wish}
for a single run, and use the range specified by \parlink{psiHat\_min} and \parlink{psiHat\_max} for radial scans.\\

{\ttfamily inputRadialCoordinate}==1: Use the flux surface specified by \parlink{psiN\_wish}
for a single run, and use the range specified by \parlink{psiN\_min} and \parlink{psiN\_max} for radial scans.\\

{\ttfamily inputRadialCoordinate}==2: Use the flux surface specified by \parlink{rHat\_wish}
for a single run, and use the range specified by \parlink{rHat\_min} and \parlink{rHat\_max} for radial scans.\\

{\ttfamily inputRadialCoordinate}==3: Use the flux surface specified by \parlink{rN\_wish}
for a single run, and use the range specified by \parlink{rN\_min} and \parlink{rN\_max} for radial scans. \\

@@

\param{psiHat\_wish}
{real}
{-1}
{Only when \parlink{inputRadialCoordinate} == 0 and \parlink{geometryScheme} == 1, 5, 11, or 12.}
{Requested flux surface for the computation.  See section \ref{sec:radialCoordinates}
for more information about radial coordinates.}

@@

\param{psiN\_wish}
{real}
{0.25}
{Only when \parlink{inputRadialCoordinate} == 1 and \parlink{geometryScheme} == 1, 5, 11, or 12.}
{Requested flux surface for the computation.  See section \ref{sec:radialCoordinates}
for more information about radial coordinates.}

@@

\param{rHat\_wish}
{real}
{-1}
{Only when \parlink{inputRadialCoordinate} == 2 and \parlink{geometryScheme} == 1, 5, 11, or 12.}
{Requested flux surface for the computation.  See section \ref{sec:radialCoordinates}
for more information about radial coordinates.}

@@

\param{rN\_wish}
{real}
{0.5}
{Only when \parlink{inputRadialCoordinate} == 3 and \parlink{geometryScheme} == 1, 5, 11, or 12.}
{Requested flux surface for the computation.  See section \ref{sec:radialCoordinates}
for more information about radial coordinates.}

@@

\param{GHat}
{real}
{3.7481}
{Only when \parlink{geometryScheme} == 1 or 13. Otherwise, {\ttfamily GHat} will be set according to the requested \parlink{geometryScheme}.}
{$G$ is $(c/2)\times$ the poloidal current outside the flux
 surface. Equivalently, $G$ is the coefficient of $\nabla\zeta_B$ in the
 covariant representation of $\vect{B}$ in terms of Boozer coordinates $(\theta_B,\zeta_B)$:
\begin{equation}
\label{eq:covariant}
\vect{B}(\psi,\theta_B,\zeta_B) = \beta(\psi,\theta_B,\zeta_B)\nabla\psi + I(\psi)\nabla\theta_B + G(\psi)\nabla\zeta_B.
\end{equation}
{\ttfamily GHat} is $G$ normalized by $\bar{B}\bar{R}$.}

@@

\param{IHat}
{real}
{0.0}
{Only when \parlink{geometryScheme} == 1 or 13. Otherwise, {\ttfamily IHat} will be set according to the requested \parlink{geometryScheme}.}
{$I$ is $(c/2)\times$ the toroidal current inside the flux
 surface. Equivalently, $I$ is the coefficient of $\nabla\theta_B$ in the
 covariant representation of $\vect{B}$ in terms of Boozer coordinates $(\theta_B,\zeta_B)$ in (\ref{eq:covariant}).
{\ttfamily IHat} is $I$ normalized by $\bar{B}\bar{R}$.}

@@

\param{iota}
{real}
{0.4542}
{Only when \parlink{geometryScheme} == 1 or 13. Otherwise, {\ttfamily iota} will be set according to the requested \parlink{geometryScheme}.}
{Rotational transform (rationalized), equivalent to $1/q$ where $q$ is the safety factor.}

@@

\param{epsilon\_t}
{real}
{-0.07053}
{Only when \parlink{geometryScheme} == 1.}
{Toroidal variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\param{epsilon\_h}
{real}
{0.05067}
{Only when \parlink{geometryScheme} == 1.}
{Helical variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\param{epsilon\_antisymm}
{real}
{0.0}
{Only when \parlink{geometryScheme} == 1.}
{Stellarator-antisymmetric variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\param{helicity\_l}
{integer}
{2}
{Only when \parlink{geometryScheme} == 1.}
{Poloidal mode number of the helical variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\param{helicity\_n}
{integer}
{10}
{Only when \parlink{geometryScheme} == 1.}
{Toroidal mode number of the helical variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\param{helicity\_antisymm\_l}
{integer}
{1}
{Only when \parlink{geometryScheme} == 1.}
{Poloidal mode number of the stellarator-antisymmetric variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\param{helicity\_antisymm\_n}
{integer}
{0}
{Only when \parlink{geometryScheme} == 1.}
{Toroidal mode number of the stellarator-antisymmetric variation in $B$, as defined by (\ref{eq:Bmodel}).
Note that you can create an up-down asymmetric tokamak by setting \parlink{helicity\_antisymm\_n}=0, \parlink{epsilon\_h}=0,
and \parlink{epsilon\_antisymm}$>$0.}

@@

\param{VMEC\_Nyquist\_option}
{integer}
{1}
{Only when \parlink{geometryScheme} == 5.}
{In VMEC, some quantities are known at poloidal and toroidal mode numbers given by the arrays {\ttfamily xm} and
{\ttfamily xn}, whereas other quantities are known at a larger range of mode numbers {\ttfamily xm\_nyq} and {\ttfamily xn\_nyq}.
The sfincs parameter {\ttfamily VMEC\_Nyquist\_option}
controls whether or not to include mode numbers that exist in the {\ttfamily xm\_nyq} and {\ttfamily xn\_nyq}
arrays but not in the {\ttfamily xm} and {\ttfamily xn} arrays.
This this parameter only affects high-frequency components of the magnetic field, results of sfincs
should not be very sensitive to this parameter.
\\

@@

\param{min\_Bmn\_to\_load}
{real}
{0.0}
{Only when \parlink{geometryScheme} == 5, 11, or 12.}
{Filters the magnetic field read from an input file.  Only Fourier modes $(m,n)$ for which $B_{m,n}$ is at least {\ttfamily min\_Bmn\_to\_load} will be included.}

@@

\param{rippleScale}
{real}
{1.0}
{Only when \parlink{geometryScheme}==5. \parlink{helicity\_l} and \parlink{helicity\_n} must be specified.}
{Scales the values of components of VMEC geometry (modes of $B$, $B^{u}$, $B_{u}$, $B^{v}$, $B_{v}$, $B_{s}$, and $\sqrt{g}$) that do not satisfy a desired symmetry. If \parlink{helicity\_n}$==0$, modes for which $n \neq 0$ or $m \neq$ \parlink{helicity\_l} are multiplied by \parlink{rippleScale}. If \parlink{helicity\_n}$\neq0$, modes for which $m/n \neq$ \parlink{helicity\_l}/\parlink{helicity\_n} or $n==0$ are multiplied by \parlink{rippleScale}. All other modes remain unchanged.}

@@

\param{EParallelHatSpec\_bcdatFile}
{string}
{``''}
{Only when \parlink{EParallelHatSpec} is non-zero
  and \parlink{RHSmode}==1 \\and \parlink{EParallelHatSpec\_bcdatFile}
  is not == ``''}
{When set this loads a file which looks like a bc file, but with the
  part which usually contains Fourier coefficients for
  $R$,$Z$,$B$,\ldots instead contains the coefficients for a function
  which will multiply the ``effective parallel electric fields'' \parlink{EParallelHatSpec}
  (otherwise just proportional to $B$).}

\param{boozer\_bmnc}
{2D array of reals}
{0}
{Only when \parlink{geometryScheme} == 13. }
{Fourier harmonics describing the magnetic field in Boozer coordinates,
\begin{gather}
B(\theta_B,\zeta_B) = \sum_{m,n}\mathrm{\texttt{boozer\_bmnc}}(m,n) \cos(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B),
\end{gather}
The first index of \texttt{ Boozer\_bmnc} corresponds to $m \in $[0,\parlink{mmax\_boozer}], and the second corresponds to $n \in $[-\parlink{nmax\_boozer},\parlink{nmax\_boozer}]. Here \parlink{Nperiods} can be specified in the input file.
}

\param{mmax\_boozer}
{integer}
{40}
{Only when \parlink{geometryScheme} == 13.}
{Boozer geometry is described for $m \leq $ \texttt{mmax\_boozer}. }

\param{nmax\_boozer}
{integer}
{40}
{Only when \parlink{geometryScheme} == 13.}
{Boozer geometry is described for $|n| \leq $ \texttt{nmax\_boozer}. }

\param{Nperiods}
{integer}
{0}
{Only when \parlink{geometryScheme} == 13.}
{Boozer geometry will assume number of periods is \texttt{Nperiods}.}

@@

\param{withAdiabatic}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true}
{If this parameter is \true, an adiabatic species is added into the quasineutrality equation (but has no other effect).}

@@

\param{adiabaticZ}
{real}
{-1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{withAdiabatic} == \true}
{Charge of adiabatic species, in units of the proton charge $e$.}

@@

\param{adiabaticMHat}
{real}
{5.44617e-4}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{withAdiabatic} == \true}
{Mass of adiabatic species, in units of the reference mass $\bar{m}$.}

@@

\param{adiabaticNHat}
{real}
{1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{withAdiabatic} == \true}
{Density of adiabatic species, in units of the reference density $\bar{n}$.}

@@

\param{adiabaticTHat}
{real}
{1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{withAdiabatic} == \true}
{Temperature of adiabatic species, in units of the reference temperature $\bar{T}$.}

@@

\param{withNBIspec} {Boolean} {\false} {Whenever \parlink{RHSMode} ==
  1 and \parlink{includePhi1} == \true\\
  ~and \parlink{quasineutralityOption} == 1} {When this is \true, an
  extra species (here called NBIspec) is added to the quasineutrality
  condition, but not as a species for which the DKE is solved. This is
  to mimic how the fast ions influence the other species via the
  $\phi_1$ variation on the flux surface. (The influence via
  collisions can be modelled using \parlink{EParallelHatSpec}). The
  NBIspec is assumed to have a density distribution on the flux suface
  proportional to $B$ (which is the case if all particles have zero
  pitch angle).}

@@

\param{NBIspecZ}
{real}
{1.0}
{Whenever \parlink{withNBIspec}== \true~ and \parlink{RHSMode} == 1 \\
  and \parlink{includePhi1} == \true~ and \parlink{quasineutralityOption} == 1}
{Charge of the fast ion species, in units of the proton charge $e$, see \parlink{withNBIspec}.}

@@

\param{NBIspecNHat}
{real}
{0.0}
{Whenever \parlink{withNBIspec}== \true~ and \parlink{RHSMode} == 1 \\
and \parlink{includePhi1} == \true~ and \parlink{quasineutralityOption} == 1}
{Density of the fast ion species, in units of the reference density
  $\bar{n}$, see \parlink{withNBIspec}. \todo{Implement possibility to load a bcdat file with the
  fast ion density distribution on the flux surfaces}}

@@

\param{nuPrime}
{real}
{1.0}
{Only when \parlink{RHSMode} == 3.}
{Dimensionless collisionality used in place of \parlink{nHats}, \parlink{THats}, \parlink{mHats}, \parlink{Zs}, and \parlink{nu\_n} for computing monoenergetic transport coefficients.
See section \ref{sec:monoenergetic} for more details.}

@@

{\ttfamily collisionOperator} = 1: Pitch-angle scattering operator (with no momentum-conserving field term).
}}

@@

\param{include\_fDivVE\_term}
{Boolean}
{\false}
{Never}
{Obsolete}

@@

\param{includePhi1inKineticEquation}
{Boolean}
{\true}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true}
{If true, the terms containing $\Phi_1$ will be included in the kinetic equation. 
If false, and \parlink{includePhi1} = \true, then $\Phi_1$ is only included in the quasineutrality equation. 
}

>>>>

\newcommand{\param}[5]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#1}{#1}}\\{\it Type}: #2\\{\it Default}: #3\\{\it When it matters}: #4\\{\it Meaning}: #5}}
%%NOTE BY AM, the \param command does not work for defining parameters with an underscore in the name, for these parameters use \paramWithUnderscore.
\newcommand{\paramWithUnderscore}[6]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#2}{#1}}\\{\it Type}: #3\\{\it Default}: #4\\{\it When it matters}: #5\\{\it Meaning}: #6}}
\newcommand{\ssparam}[4]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#1}{#1}}\\{\it Type}: #2\\{\it When it matters}: #3\\{\it Meaning}: #4}}
\newcommand{\ssparamWithUnderscore}[5]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries \hypertarget{#2}{#1}}\\{\it Type}: #3\\{\it When it matters}: #4\\{\it Meaning}: #5}}
\newcommand{\PETScParam}[2]{{\setlength{\parindent}{0cm} {\ttfamily \bfseries #1}\\{\it Meaning}: #2}}
\newcommand{\myhrule}{{\setlength{\parindent}{0cm} \hrulefill }}

@@

{\ttfamily RHSMode} = 2: Solve for 3 right-hand sides to get the 3$\times$3 transport matrix. Presently implemented only for 1 species and \parlink{includePhi1} == \false\\

{\ttfamily RHSMode} = 3: Solve for the 2$\times$2 monoenergetic transport coefficients. When this option is chosen, \Nx~is set to 1, only 1 species is used and \parlink{includePhi1} is set to \false
}

@@

@@

{\ttfamily geometryScheme}==1: Use the following 3-helicity model:\\
\begin{eqnarray}
\label{eq:Bmodel}
B(\theta,\zeta)/\bar{B} 
&=& (\mbox{\parlink{B0OverBBar}}) [1 + (\mbox{\underscoreparlink{epsilon\_t}{epsilon_t}}) \cos(\theta) \\
&& + (\mbox{\underscoreparlink{epsilon\_h}{epsilon_h}}) \cos((\mbox{\underscoreparlink{helicity\_l}{helicity_l}}) \theta - (\mbox{\underscoreparlink{helicity\_n}{helicity_n}}) \zeta) \nonumber \\
&&  + (\mbox{\underscoreparlink{epsilon\_antisymm}{epsilon_antisymm}}) \nonumber \\
&& \times \sin((\mbox{\underscoreparlink{helicity\_antisymm\_l}{helicity_antisymm_l}}) \theta - (\mbox{\underscoreparlink{helicity\_antisymm\_n}{helicity_antisymm_n}}) \zeta)] \nonumber
\end{eqnarray}

@@

{\ttfamily geometryScheme}==12: Read the IPP {\ttfamily .bc} format Boozer-coordinate file specified in \parlink{equilibriumFile} below. 
The file is assumed to be stellarator-\emph{asymmetric}.
}

@@

{\ttfamily inputRadialCoordinate}==0: Use the flux surface specified by \underscoreparlink{psiHat\_wish}{psiHat_wish}
for a single run, and use the range specified by \underscoreparlink{psiHat\_min}{psiHat_min} and \underscoreparlink{psiHat\_max}{psiHat_max} for radial scans.\\

{\ttfamily inputRadialCoordinate}==1: Use the flux surface specified by \underscoreparlink{psiN\_wish}{psiN_wish}
for a single run, and use the range specified by \underscoreparlink{psiN\_min}{psiN_min} and \underscoreparlink{psiN\_max}{psiN_max} for radial scans.\\

{\ttfamily inputRadialCoordinate}==2: Use the flux surface specified by \underscoreparlink{rHat\_wish}{rHat_wish}
for a single run, and use the range specified by \underscoreparlink{rHat\_min}{rHat_min} and \underscoreparlink{rHat\_max}{rHat_max} for radial scans.\\

{\ttfamily inputRadialCoordinate}==3: Use the flux surface specified by \underscoreparlink{rN\_wish}{rN_wish}
for a single run, and use the range specified by \underscoreparlink{rN\_min}{rN_min} and \underscoreparlink{rN\_max}{rN_max} for radial scans. \\

@@

\paramWithUnderscore{psiHat\_wish}{psiHat_wish}
{real}
{-1}
{Only when \parlink{inputRadialCoordinate} == 0 and \parlink{geometryScheme} == 1, 5, 11, or 12.}
{Requested flux surface for the computation.  See section \ref{sec:radialCoordinates}
for more information about radial coordinates.}

@@

\paramWithUnderscore{psiN\_wish}{psiN_wish}
{real}
{0.25}
{Only when \parlink{inputRadialCoordinate} == 1 and \parlink{geometryScheme} == 1, 5, 11, or 12.}
{Requested flux surface for the computation.  See section \ref{sec:radialCoordinates}
for more information about radial coordinates.}

@@

\paramWithUnderscore{rHat\_wish}{rHat_wish}
{real}
{-1}
{Only when \parlink{inputRadialCoordinate} == 2 and \parlink{geometryScheme} == 1, 5, 11, or 12.}
{Requested flux surface for the computation.  See section \ref{sec:radialCoordinates}
for more information about radial coordinates.}

@@

\paramWithUnderscore{rN\_wish}{rN_wish}
{real}
{0.5}
{Only when \parlink{inputRadialCoordinate} == 3 and \parlink{geometryScheme} == 1, 5, 11, or 12.}
{Requested flux surface for the computation.  See section \ref{sec:radialCoordinates}
for more information about radial coordinates.}

@@

\param{GHat}
{real}
{3.7481}
{Only when \parlink{geometryScheme} == 1. Otherwise, {\ttfamily GHat} will be set according to the requested \parlink{geometryScheme}.}
{$G$ is $(c/2)\times$ the poloidal current outside the flux
 surface. Equivalently, $G$ is the coefficient of $\nabla\zeta_B$ in the
 covariant representation of $\vect{B}$ in terms of Boozer coordinates $(\theta_B,\zeta_B)$:
\begin{equation}
\label{eq:covariant}
\vect{B}(\psi,\theta_B,\zeta_B) = \beta(\psi,\theta_B,\zeta_B)\nabla\psi + I(\psi)\nabla\theta_B + G(\psi)\nabla\zeta_B.
\end{equation}
{\ttfamily GHat} is $G$ normalized by $\bar{B}\bar{R}$.}

@@

\param{IHat}
{real}
{0.0}
{Only when \parlink{geometryScheme} == 1. Otherwise, {\ttfamily IHat} will be set according to the requested \parlink{geometryScheme}.}
{$I$ is $(c/2)\times$ the toroidal current inside the flux
 surface. Equivalently, $I$ is the coefficient of $\nabla\theta_B$ in the
 covariant representation of $\vect{B}$ in terms of Boozer coordinates $(\theta_B,\zeta_B)$ in (\ref{eq:covariant}).
{\ttfamily IHat} is $I$ normalized by $\bar{B}\bar{R}$.}

@@

\param{iota}
{real}
{0.4542}
{Only when \parlink{geometryScheme} == 1. Otherwise, {\ttfamily iota} will be set according to the requested \parlink{geometryScheme}.}
{Rotational transform (rationalized), equivalent to $1/q$ where $q$ is the safety factor.}

@@

\paramWithUnderscore{epsilon\_t}{epsilon_t}
{real}
{-0.07053}
{Only when \parlink{geometryScheme} == 1.}
{Toroidal variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\paramWithUnderscore{epsilon\_h}{epsilon_h}
{real}
{0.05067}
{Only when \parlink{geometryScheme} == 1.}
{Helical variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\paramWithUnderscore{epsilon\_antisymm}{epsilon_antisymm}
{real}
{0.0}
{Only when \parlink{geometryScheme} == 1.}
{Stellarator-antisymmetric variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\paramWithUnderscore{helicity\_l}{helicity_l}
{integer}
{2}
{Only when \parlink{geometryScheme} == 1, or when simultaneously \parlink{geometryScheme} == 5 and \parlink{rippleScale} != 1.0.}
{Poloidal mode number of the helical variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\paramWithUnderscore{helicity\_n}{helicity_n}
{integer}
{10}
{Only when \parlink{geometryScheme} == 1, or when simultaneously \parlink{geometryScheme} == 5 and \parlink{rippleScale} != 1.0.}
{Toroidal mode number of the helical variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\paramWithUnderscore{helicity\_antisymm\_l}{helicity_antisymm_l}
{integer}
{1}
{Only when \parlink{geometryScheme} == 1.}
{Poloidal mode number of the stellarator-antisymmetric variation in $B$, as defined by (\ref{eq:Bmodel}).}

@@

\paramWithUnderscore{helicity\_antisymm\_n}{helicity_antisymm_n}
{integer}
{0}
{Only when \parlink{geometryScheme} == 1.}
{Toroidal mode number of the stellarator-antisymmetric variation in $B$, as defined by (\ref{eq:Bmodel}).
Note that you can create an up-down asymmetric tokamak by setting \underscoreparlink{helicity\_antisymm\_n}{helicity_antisymm_n}=0, \underscoreparlink{epsilon\_h}{epsilon_h}=0,
and \underscoreparlink{epsilon\_antisymm}{epsilon_antisymm}$>$0.}

@@

\paramWithUnderscore{VMEC\_Nyquist\_option}{VMEC_Nyquist_option}
{integer}
{1}
{Only when \parlink{geometryScheme} == 5.}
{In VMEC, some quantities are known at poloidal and toroidal mode numbers given by the arrays {\ttfamily xm} and
{\ttfamily xn}, whereas other quantities are known at a larger range of mode numbers {\ttfamily xm\_nyq} and {\ttfamily xn\_nyq}.
The sfincs parameter {\ttfamily VMEC\_Nyquist\_option}
controls whether or not to include mode numbers that exist in the {\ttfamily xm\_nyq} and {\ttfamily xn\_nyq}
arrays but not in the {\ttfamily xm} and {\ttfamily xn} arrays.
This parameter only affects high-frequency components of the magnetic field, results of sfincs
should not be very sensitive to this parameter.
\\

@@

\paramWithUnderscore{min\_Bmn\_to\_load}{min_Bmn_to_load}
{real}
{0.0}
{Only when \parlink{geometryScheme} == 5, 11, or 12.}
{Filters the magnetic field read from an input file.  Only Fourier modes $(m,n)$ for which $B_{m,n}$ is at least {\ttfamily min\_Bmn\_to\_load} will be included.}

@@

\param{rippleScale}
{real}
{1.0}
{Only when \parlink{geometryScheme} == 5. \underscoreparlink{helicity\_l}{helicity_l} and \underscoreparlink{helicity\_n}{helicity_n} must be specified.}
{Scales the values of components of VMEC geometry (modes of $B$, $B^{u}$, $B_{u}$, $B^{v}$, $B_{v}$, $B_{s}$, and $\sqrt{g}$) that do not satisfy a desired symmetry. If \underscoreparlink{helicity\_n}{helicity_n}$==0$, modes for which $n \neq 0$ or $m \neq$ \underscoreparlink{helicity\_l}{helicity_l} are multiplied by \parlink{rippleScale}. If \underscoreparlink{helicity\_n}{helicity_n}$\neq0$, modes for which $m/n \neq$ \underscoreparlink{helicity\_l}{helicity_l}/\underscoreparlink{helicity\_n}{helicity_n} or $n==0$ are multiplied by \parlink{rippleScale}. All other modes remain unchanged.}

@@

\paramWithUnderscore{EParallelHatSpec\_bcdatFile}{EParallelHatSpec_bcdatFile}
{string}
{``''}
{Only when \parlink{EParallelHatSpec} is non-zero
  and \parlink{RHSmode}==1 \\and \underscoreparlink{EParallelHatSpec\_bcdatFile}{EParallelHatSpec_bcdatFile}
  is not == ``''}
{When set this loads a file which looks like a bc file, but with the
  part which usually contains Fourier coefficients for
  $R$,$Z$,$B$,\ldots instead contains the coefficients for a function
  which will multiply the ``effective parallel electric fields'' \parlink{EParallelHatSpec}
  (otherwise just proportional to $B$).}

@@

\param{withAdiabatic}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and\\ \parlink{readExternalPhi1} == \false}
{If this parameter is \true, an adiabatic species is added into the quasineutrality equation (but has no other effect).}

@@

\param{adiabaticZ}
{real}
{-1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and\\ \parlink{readExternalPhi1} == \false and \parlink{withAdiabatic} == \true}
{Charge of adiabatic species, in units of the proton charge $e$.}

@@

\param{adiabaticMHat}
{real}
{5.44617e-4}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and\\ \parlink{readExternalPhi1} == \false and \parlink{withAdiabatic} == \true}
{Mass of adiabatic species, in units of the reference mass $\bar{m}$.}

@@

\param{adiabaticNHat}
{real}
{1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and\\ \parlink{readExternalPhi1} == \false and \parlink{withAdiabatic} == \true}
{Density of adiabatic species, in units of the reference density $\bar{n}$.}

@@

\param{adiabaticTHat}
{real}
{1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and\\ \parlink{readExternalPhi1} == \false and \parlink{withAdiabatic} == \true}
{Temperature of adiabatic species, in units of the reference temperature $\bar{T}$.}

@@

\param{withNBIspec} {Boolean} {\false} {Whenever \parlink{RHSMode} ==
  1 and \parlink{includePhi1} == \true and\\
  \parlink{readExternalPhi1} == \false and \parlink{quasineutralityOption} == 1} {When this is \true, an
  extra species (here called NBIspec) is added to the quasineutrality
  condition, but not as a species for which the DKE is solved. This is
  to mimic how the fast ions influence the other species via the
  $\phi_1$ variation on the flux surface. (The influence via
  collisions can be modelled using \parlink{EParallelHatSpec}). The
  NBIspec is assumed to have a density distribution on the flux suface
  proportional to $B$ (which is the case if all particles have zero
  pitch angle).}

@@

\param{NBIspecZ}
{real}
{1.0}
{Whenever \parlink{withNBIspec}== \true and \parlink{RHSMode} == 1 and \parlink{includePhi1}\\
   == \true and \parlink{readExternalPhi1} == \false and \parlink{quasineutralityOption} == 1}
{Charge of the fast ion species, in units of the proton charge $e$, see \parlink{withNBIspec}.}

@@

\param{NBIspecNHat}
{real}
{0.0}
{Whenever \parlink{withNBIspec}== \true and \parlink{RHSMode} == 1 and \parlink{includePhi1} \\
== \true and \parlink{readExternalPhi1} == \false and \parlink{quasineutralityOption} == 1}
{Density of the fast ion species, in units of the reference density
  $\bar{n}$, see \parlink{withNBIspec}. \todo{Implement possibility to load a bcdat file with the
  fast ion density distribution on the flux surfaces}}

@@

\param{nuPrime}
{real}
{1.0}
{Only when \parlink{RHSMode} == 3.}
{Dimensionless collisionality used in place of \parlink{nHats}, \parlink{THats}, \parlink{mHats}, \parlink{Zs}, and \underscoreparlink{nu\_n}{nu_n} for computing monoenergetic transport coefficients.
See section \ref{sec:monoenergetic} for more details.}

@@

{\ttfamily collisionOperator} = 1: Pitch-angle scattering operator (with no momentum-conserving field term).
}\newline
\newline
See section~\ref{sec:CollisionOperator} for more details about the collision operator.}

@@

\paramWithUnderscore{include\_fDivVE\_term}{include_fDivVE_term}
{Boolean}
{\false}
{Never}
{Obsolete}

@@

\param{readExternalPhi1}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true}
{If true, \parlink{Phi1Hat} is read from the HDF5 file specified by \parlink{externalPhi1Filename}, 
the quasineutrality equation and the condition $\left<\Phi_1\right> = 0$ are ignored and the solved system is linear.
If true, and \parlink{includePhi1InKineticEquation} = \false, then $\Phi_1$ does not appear anywhere in the system of equations, 
and $f_{s1}$ is unaffected by $\Phi_1$. 
However, the fluxes are still affected by $\Phi_1$ (see section~\ref{sec:RadialFluxesAndFlows}).
}
